\documentclass[letterpaper, 12 pt, conference]{ieeeconf}


\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}  % for \DeclareMathOperator macro
\IEEEoverridecommandlockouts   


\title{\LARGE \bf
ROB514-HW4: Is Autonomous Robot Revolution True?}
\author{Xi Yu}
\date{December 2015}


\begin{document}

\maketitle

\section{Autonomous robot should be used in the military}
Autonomous robots are becoming more and more useful in the military. Big dog is a good example, which is able to walk through any surfaces and carry heavy materials for a soldier team [1]. Solders in Iraq and Afghanistan routinely carry over 60-pound equipment in their backpacks [2]. This brings solders much pains when they walk for hours, and they might lose too much energy before a skirmish. A tired solder is much more possible to lose his life. Thus, an autonomous, like Big Dog, helps to carry solders’ gear and save solders’ energy. Consequentially, it assist solders to win a combat. 

Different to normal firearms, autonomous robots are not just tools, robots can recognize enemies and allies. Thus, there is lower probability that our robots become tourists’ weapons. 

Our military aims to protect our country and people not to be harmed by tourists who unethically kill innocent people. Autonomous robot should be used to fight back in order to avoid more injuries and deaths on innocent people and the soldiers who stand out to fight with tourists.

\section{Autonomous robot should never be used in the military}
Robots are machines. Our solders can give robot orders, so can tourists. Technically, there is not a computer system that is perfectly safe to against hacking. Thus, autonomous robots are initially designed to follow right order, but they might be used by bad people. In the military, autonomous robots are used to kill people or assist to kill people. It is obviously not ethical. Since an autonomous robots are self-controlling system, it has the ability to decide to harm people or not. Essentially, robots are not equal to human. A robot can never have full human sense. Therefore, autonomous robot should never judge if it is necessary to eliminate a human. Even human can never judge it. 

\section{Will robots steal our jobs or create more jobs?}
Some people worry about that robots will steal human’s jobs in the future. In Martin Ford’s book, Rise of the robots, he says that intelligent robot will soon overhaul our economy because they are showing awesome productivity and retention rates. Oxford University researcher have estimated that 47 percent of U.S. jobs well be taken by autonomous robots within the next two decades [3]. Pistono thinks that “computer power is growing exponentially, and it is advancing efforts to mechanize the labor force”. In the past 60 years, computer speed doubles every three years, and the speed is growing faster. Thus, a revolution that autonomous robots replace human labors is happening [4].

Some people think robot will create more jobs for human. Dylon Love believes that robots will never take our jobs. One of his support is that Tesla's numerous robots help facilitate the construction of its electric cars, completing the assembly of one car part an average of every six seconds. But Tesla has also added 6,000 human jobs [5]. 

In my opinion, it dependents on the job fields. In the future, robots will replace all the low level labors. Low level work means repeated work that needs less skills. Human will do higher level works that are more creative. For example, most people will have high education and be able to design robot for production. Some people will do the job of repairing and maintaining robots. Consequently, the more robots our market needs, the more human jobs will be posted to design and maintain the robots. In a big picture, our job will not become less. They just change to another field. 

\begin{thebibliography}{99}
\bibitem{c1} BigDog - The Most Advanced Rough-Terrain Robot on Earth. Boston Dynamics. Retrieved 2009-06-22.Available: http://www.bostondynamics.com/
\bibitem{c2} Weight Of War: Soldiers' Heavy Gear Packs On Pain Available: http://www.npr.org
\bibitem{c3}Rise of the Machines: The Future has Lots of Robots, Few Jobs for Humans  Available: http://www.wired.com
\bibitem{c4}P. Federico. (2014). Get ready, robots are going to steal your job Available: http://www.cnbc.com/

\bibitem{c5}L. Dylan. (2014). This Settles The 'Robots Will Take Our Jobs' Argument Once And For All  Available: http://www.businessinsider.com


\end{thebibliography}


\end{document}
